SemanticPaint

### 2015-12-08 cv3d_seminar/presentation.tex
some updates

%---------------------------------------------------------------------------------------
\section{Introduction}
\begin{frame}
\frametitle{Introduction}

@@

%---------------------------------------------------------------------------------------
\section{State of the Art}
\begin{frame}
\frametitle{Acquisition and Reconstruction}

@@

@@

%---------------------------------------------------------------------------------------
\section{Pipeline}
\begin{frame}
\frametitle{Voxel Oriented Patch features}

@@

\begin{frame}
\frametitle{Streaming Random Forest}
\end{frame}

\begin{frame}
\frametitle{SRF - Reservoir Splitting}

\begin{figure}[!ht]
  \center
  \includegraphics[width=\textwidth]{figures/forest}
%   \caption{Splitting reservoirs in Streaming Random Forest.}
  \label{fig:forest}
\end{figure}

@@

  \begin{equation} \label{eq:posterior}
  P(\mathbf{x}|\mathbf{D}) = \prod_{i \in \mathcal{V}} \left( \psi_i(x_i) \prod_{j \in \mathcal{E}_i} \psi_{ij}(x_i, x_j) \right) 
  \end{equation}

  \begin{equation} \label{eq:energy}
  E_t(\mathbf{x}) = \sum_{i \in \mathcal{V}} \left( \phi_i(x_i) + \sum_{j \in \mathcal{E}_i} \phi_{ij} (x_i, x_j) \right) + K
  \end{equation}

@@

\begin{frame}
\frametitle{CRF - User Interactions}

  Touching:
  \begin{equation}
  \phi_i(l) =
    \begin{cases}
      0      & \quad \text{if } l = l_S\\
      \infty  & \quad \text{otherwise}\\
    \end{cases}
  \end{equation}

  Encircling:
  \begin{equation}
  \phi_i(l) =
    \begin{cases}
      \log P_E(fg|\mathbf{a}_i)       & \quad \text{if } l = \text{fg}\\
      \log (1 - P_E(fg|\mathbf{a}_i))  & \quad \text{if } l = \text{bg}\\
    \end{cases}
  \end{equation}

@@

  Predictions:
  \begin{equation}
  \phi_i(l) = -\log P_F(x_i = l | \mathbf{D})
  \end{equation}

  Smoothnes:
  \begin{equation}
      \phi_{ij}(x_i, x_j)  = \theta_p e^{-||\mathbf{p}_i - \mathbf{p}_j||}  + \theta_a e^{-||\mathbf{a}_i - \mathbf{a}_j||} + \theta_n e^{-||\mathbf{n}_i - \mathbf{n}_j||}
  \end{equation}
\end{frame}

\begin{frame}
\frametitle{Mean-Field Inference}
$P(\mathbf{x})$ approximated by $Q(\mathbf{x})$ under $KL(Q||P)$:
\begin{equation}
 Q_i^t(l) = \frac{1}{Z_i}e^{M_i(l)} \text{, } t = 1, \ldots, T
\end{equation}
\begin{equation}
 M_i(l) = \phi_i(l) + \sum_{l' \in \mathcal{L}} \sum_{j \in \mathcal{N}(i)} Q_j^{t-1}(l')\phi_{ij}(l, l')
\end{equation}

@@

%---------------------------------------------------------------------------------------
\section{Results}
\begin{frame}
\frametitle{Segmentation}

@@

@@

  \item Levoy , M. et. al. 2000. The digital Michelangelo project: 3D scanning of large statues. In Proc. SIGGRAPH. ACM.

>>>>

%---------------------------------------------------------------------------------------
\section{Introduction}

%---------------------------------------------------------------------------------------
\section{State of the Art}

\begin{table}
\noindent\makebox[\linewidth]{
 \begin{tabular}{c|c|c}
  Who & What & How \\ \hline

  Valentin et. al. 2013  & inference on & RGB and geom. features  \\
  & mesh from TSDF  & CRF segmentation \\ \hline

  Kim et. al. 2013 & reconstruction & Voxel-based CRF \\ 
    & segmentation   & with visibility contraints\\ \hline

  Herbst et. al. 2014  & reconstruction & online model updates \\
     & segmentation & change detection\\ \hline

 \end{tabular}
}
\end{table}

@@

\begin{frame}
\frametitle{Model-based SLAM}

\begin{table}
\noindent\makebox[\linewidth]{
 \begin{tabular}{c|c|c}
  Who & What & How \\ \hline
  Newcombe et. al. 2011  & online 3D SLAM & model-based tracking \\
  && global TSDF volume \\ \hline

  Salas-Moreno et al. 2013 & object-level & offline object database \\
  & SLAM & pose-object graph\\ \hline

  Pradeep et.al. 2013 & 3D reconstruction & sparse tracking and  \\
    & with 1 RGB camera  & stereo reconstruction \\
    && on par with KinectFusion
 \end{tabular}
}
\end{table}

@@

%---------------------------------------------------------------------------------------
\section{Pipeline}

\begin{frame}
\frametitle{Pipeline Overview}
\begin{figure}
 \includegraphics[width=\textwidth]{figures/pipeline}
\end{figure}

@@

\begin{frame}
\frametitle{Voxel Oriented Patch features}

@@

\begin{frame}
\frametitle{Random Forest}

\begin{columns}
 \begin{column}{0.5\textwidth}
  \begin{figure}
  \center
  \includegraphics[width=\textwidth]{figures/rf}
  \caption{Single tree}
\end{figure}
 \end{column}
 \begin{column}{0.5\textwidth}
    bagged trees\\
    greedy training\\
    bootstraped data\\    
    off-line, all data at once\\
    voting for final result\\

    $(i, l) \in \mathcal{S}$ - (voxel, label) pairs\\
    $f(i, \theta)$ - split functions\\
    $\Theta$ - distribution of split functions\\
    $P_F(x_i = l | \mathbf{D})$ - class conditional probability\\
 \end{column}

\begin{frame}
\frametitle{Streaming Random Forest}
  \begin{itemize}
   \item Node n: Reservoir $R_n$ with a list of samples $T_n$, $|T_n| \leq K$
   \item First $K$ samples added
   \item Current samples swapped with new ones with decreasing probability
   \item Split node if: $|R_n| > N$
  \end{itemize}

  Information Gain:
  \vspace{-0.25cm}
  \begin{equation} \label{eq:infogain}
    G(R_n, R_n^L, R_n^R) = H(R_n) - \sum_{d \in \{L, R\}} \frac{|R_n^d|}{|R_n|}H(R_n^d)
  \end{equation}
  Shannon Entropy:
  \vspace{-0.25cm}
  \begin{equation}
   H(R_n) = - \sum_{(l, i) \in T_n} p(c_i = l) \log{p(c_i = l)}
  \end{equation}

  \vspace{-0.25cm}
  $H(R_n)$ computed from a node's class distribution
\end{frame}

\begin{frame}
\frametitle{SRF - Reservoir Splitting}
$m_n$ - number of samples seen at node $n$\\
$P(l | T_n)$ - normalized class distribution of $R_n$
\vspace{-0.25cm}
\begin{figure}[!ht]
  \center
  \includegraphics[width=\textwidth]{figures/forest}
%   \caption{Splitting reservoirs in Streaming Random Forest.}
  \label{fig:forest}
\end{figure}

@@

Joint class probability distribution for the volume $\mathcal{V}$:
  \begin{equation} \label{eq:posterior}
  P(\mathbf{x}|\mathbf{D}) = \prod_{i \in \mathcal{V}} \left( \psi_i(x_i) \prod_{j \in \mathcal{E}_i} \psi_{ij}(x_i, x_j) \right) 
  \end{equation}

\vspace{-0.5cm}
Labeling Energy at time $t$:
  \begin{equation} \label{eq:energy}
  E_t(\mathbf{x}) = \sum_{i \in \mathcal{V}} \left( \phi_i(x_i) + \sum_{j \in \mathcal{E}_i} \phi_{ij} (x_i, x_j) \right) + K
  \end{equation}

\vspace{-0.5cm}  
where:\\
$\phi_i(x_i)$ - cost of assigning a label \\
$\phi_{ij}(x_i, x_j)$ - cost of assuming different labels\\
$\mathcal{E}_i$ - neighbourhood of voxel $i$

@@

\begin{frame}
\frametitle{CRF - User Interactions}
% \vspace{-1cm}
  Touching:
  \begin{columns}
   \begin{column}{0.25\textwidth}
    \begin{figure}
    \includegraphics[width=\textwidth]{figures/touch}
    \end{figure}
    \end{column}
    \begin{column}{0.75\textwidth}
      \begin{equation}
	\phi_i(l) =
	  \begin{cases}
	    0      & \quad \text{if } l = l_T\\
	    \infty  & \quad \text{otherwise}\\
	  \end{cases}
      \end{equation}
      \center
      $T$ --- touched pixels
   \end{column}

  \end{columns}

  \vspace{0.5cm}
  Encircling:
  \vspace{-0.5cm}
    \begin{columns}
   \begin{column}{0.25\textwidth}
    \begin{figure}
    \includegraphics[width=\textwidth]{figures/circle}
    \end{figure}
   \end{column}
    \begin{column}{0.75\textwidth}
      \begin{equation}
  \phi_i(l) =
    \begin{cases}
      \log P_E(fg|\mathbf{a}_i)       & \quad \text{if } l = \text{fg}\\
      \log (1 - P_E(fg|\mathbf{a}_i))  & \quad \text{if } l = \text{bg}\\
    \end{cases}
  \end{equation}

  \center
  $P_E$ from GMM\\
  fg --- inside\\
  bg --- outside
   \end{column}

  \end{columns}

@@

  Predictions:
  \begin{equation}
  \phi_i(l) = -\log P_F(x_i = l | \mathbf{D})
  \end{equation}
  $P_F$ --- Streaming Random Forest prediction

  \vspace{0.5cm}
  Smoothnes:
  \begin{equation}
      \phi_{ij}(x_i, x_j)  = \theta_p e^{-||\mathbf{p}_i - \mathbf{p}_j||}  + \theta_a e^{-||\mathbf{a}_i - \mathbf{a}_j||} + \theta_n e^{-||\mathbf{n}_i - \mathbf{n}_j||}
  \end{equation}

  $\theta_p$, $\theta_a$, $\theta_n$ --- paramters \\
  $\mathbf{p}_i$ --- position\\
  $\mathbf{a}_i$ --- appearance\\
  $\mathbf{n}_i$ --- normal vector

\begin{frame}
\frametitle{Mean-Field Inference}
$P(\mathbf{x})$ approximated by $Q(\mathbf{x})$ under $KL(Q||P)$:
\begin{equation}
 Q_i^t(l) = \frac{1}{Z_i}e^{M_i(l)} \text{, } t = 1, \ldots, T
\end{equation}
\begin{equation}
 M_i(l) = \phi_i(l) + \sum_{l' \in \mathcal{L}} \sum_{j \in \mathcal{E}_i} Q_j^{t-1}(l')\phi_{ij}(l, l')
\end{equation}

@@

%---------------------------------------------------------------------------------------
\section{Results}
\begin{frame}
\frametitle{Segmentation}
  \begin{figure}
   \includegraphics[width=\textwidth]{figures/results}
  \end{figure}

\begin{frame}
\frametitle{Segmentation}

@@

\begin{frame}
\frametitle{Features}
\vspace{-0.25cm}
 \begin{figure}[!ht]
  \center
  \includegraphics[width=\textwidth]{figures/results_vop}
%   \caption{Average Precision}
%   \label{fig:srf_ap}
  \end{figure}
\end{frame}

@@

  \item Salas-Moreno, R. F. et. al. 2013. SLAM++: Simultaneous localisation and mapping at the level of objects. In Proc. CVPR.
